Embracing the Laws of Physics: \\ Three Reversible Models of Computation

### 2018-06-12 survey/survey.tex
.

The constructs in Fig.~\ref{figj} capture the informal idea that all
the different ways of associating programs are equivalent. For
example, a program that performs $c_1$ and then $(c_2 \odot c_3)$ can
be smoothly transformed a program that performs $(c_1 \odot c_2)$ and
then $c_3$. The last two equivalences show how several uses of
associativity interact together. For example, in the last equivalence
the program on the left $\assocrt \odot \assocrt$ transforms an input
type $((t_1 * t_2) * t_3) * t_4$ as follows:

@@

The program on the right
$((\assocrt \otimes \idc) \odot \assocrt) \odot (\idc \otimes
\assocrt)$ achieves the same end-to-end transformation using the
following sequence of steps:

@@

The equivalence states that these two sequences of steps can be
smoothly deformed to one another.

The constructs in Fig.~\ref{figi} \ldots

>>>>

The constructs in Fig.~\ref{figj} capture the informal idea that all
the different ways of associating programs are equivalent. For
example, a program that performs $c_1$ and then $(c_2 \odot c_3)$ can
be smoothly transformed a program that performs $(c_1 \odot c_2)$ and
then $c_3$. The last two equivalences show how several uses of
associativity interact together. For example, in the last equivalence
the program on the left $\assocrt \odot \assocrt$ transforms an input
type $((t_1 * t_2) * t_3) * t_4$ to an output type
$t_1 * (t_2 * (t_3 * t_4))$ as follows:

@@

\noindent The program on the right
$((\assocrt \otimes \idc) \odot \assocrt) \odot (\idc \otimes
\assocrt)$ achieves the same end-to-end transformation using the
following sequence of steps:

@@

\noindent The equivalence states that these two sequences of steps can be
smoothly deformed to one another.

The constructs in Fig.~\ref{figi} explain how choice interacts with
grouping. Intuitively, a choice nested inside a larger bundle can also
be treated as an outer choice with the nested bundle duplicated in
each branch.
